---
title: "Visitor Visa Survey Analysis"
output:
  html_document: default
classoption: landscape
fontsize: 14pt

---
```{r libs, echo=FALSE, message=FALSE, include=FALSE}
source("MastermindV2/global.R")
library(gridExtra)

```

```{r functions, echo=FALSE, message=FALSE, include=FALSE, cache=TRUE}
vv.file=read_csv("VisaDebate.csv")
names(vv.file)=c("Message", "Message", "Message")
vv.file=rbind(vv.file[,1], vv.file[,2], vv.file[,3])
vv.comments=get_comments(vv.file, "VisitorVisa")
#vv.hours=get_hours_fb(vv.file, "VisitorVisaComments")
#vv.dates=get_dates_fb(vv.file, "VisitorVisaDebate")
vv.corpus=clean_corpus(prep_corpus(vv.comments))
vv.corpus.df=get_corpus_df(vv.corpus)
vv.frequencies=term_stats(vv.corpus)
vv.dtm=get_dtm(vv.corpus)
vv.dtm.bigram=get_dtm_bigram(vv.corpus)

ud_model <- udpipe_download_model(language = "english")
ud_model <- udpipe_load_model(ud_model$file_model)
vv.ud=get_ud_data(vv.comments)
vv.8topics=get_topic_model(vv.dtm, 8)
vv.8topics.bigram=get_topic_model(vv.dtm.bigram, 8)

vv.readability=get_readability(vv.comments)
vv.ages=estimate_ages(vv.ud, vv.readability)

```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This report gives a brief summary of the textual analysis of the submissions to the Visitor Visa Survey by the Select Committee for Petitions. 

**Summary of Key Points**

  * A total of **`r nrow(vv.comments)`** comments were posted to this survey over 3 separate questions.
  * GCSE-level educated participants
  * Generally quite negative submissions with anticipation also being a common sentiment
  * Main issues raised are of the financial cost of the applications and amount of time needed to complete them. Many say their applications were rejected and concerns over family being left behind also appear often.
  


## Frequency Analysis

The comments had an average of **`r round(mean(get_each_comment_length(vv.comments)$Length))`** words in each, an average Flesch readability score of `r round(mean(vv.readability$Flesch))` suggesting readers needed to be educated to at least a UK Grade Level of `r round(mean(vv.readability$Flesch.Kincaid)) + 1` to understand the comments. As this engagement activity was in survey format, the people making submissions were educated at least to GCSE level. 

The most common adjectives, phrases and pairs of words are displayed below. People tend to express their emotions through the adjectives they use, and in this case "expensive", "financial", and "long" being used so often relate to the time and financial commitment of the application process. The key words raise issues of "health insurance" and "mental health" as other important aspects of the process. 
```{r frequencies, echo=FALSE,  tidy=TRUE, fig.width=10}
{grid.arrange(display_adjectives(vv.ud, 15), display_keywords(vv.ud, 15), ncol=2)}
```



A network of the most frequent consecutive word pairs (bigrams) is shown below. "visit visa", "application process", and "home office"
are the most common word pairs in the dataset. Phrases such as "time consuming", "bank statements", and "immigration rules" are also common and suggest pockets of comments which raise these issues often outside of the more general comments. "Children" and "grandparents" are also closely connected to the main cluster of phrases suggesting these family members are especially affected during the visa application process.


```{r bigrams, echo=FALSE, tidy=TRUE, fig.width=15, fig.height=10}
display_bigrams(vv.comments, 20, "Visitor Visa Debate")

```


***

## Topic Extraction

A plot of words most associated with one of 8 topics are shown below. Most of the topics are around the same are of.... however two topics stand out. Topic 8 is primarily about the technicalities of the application process with words such as "home office", "6 months", "application process", and "long tedious". Topic 6 is primarily about the lengthy application process and the costs associated with this, for example "paper work", "took long", "long expensive". 
<!---
A brief summary of those topics are:

Topic Number  | Common bigrams
-------- | ------------------
Topic 1  | mental health, blood sugars, life saving, self fund
Topic 2  | complete ban, trail hinting,
Topic 3  | funding needed, psychological support, available prescription, avoiding complications
Topic 4  | adult care, self management, managing condition
Topic 5  | long term, daughter diagnosed
Topic 6  | closed loop system, medical conditions, change diet, diabetes team
Topic 7  | healthcare, newly diagnosed
Topic 8  | basal insulin, checking blood, development type, weight gain
Topic 9  | postcode lottery, mental health, urine test
Topic 10  | nodeal brexit, quality of life, reassuring people, manage condition
--> 

<!---\begin{center}
\end{center}
![](Diabetes bigram topics.pdf)  


\begin{center}
\includegraphics{Diabetes bigram topics.pdf}
\end{center}
--> 

```{r, echo=FALSE}
display_top_topics(vv.8topics.bigram, 10, "Visitor Visa Debate")

```

<!--
```{r twordcloud, echo=FALSE, message=FALSE, warning=FALSE}
myColourHue= function(n=10) {
  hues = seq(15, 375, length = n + 1)
  hcl(h = hues, l = 45, c = 100)[1:n]
}
get_topic_wordcloud(vv.8topics)
```
-->



Topic model visualisations are split into two sections:

  * **Left** - showing topic distances from each other based on the types of words in each,

  * **Right** – showing the top 30 words in each topic (red bar) and overall in the dataset (blue bar). I recommend setting the relavance metric to 0.6 to get a more representative list of words in each topic.

This visualisation is interactive, hover over each topic number to view the words in each topic, or select each word to view which topics it appears.  

```{r servis, echo=FALSE, message=FALSE, warning=FALSE}
serVis(topicmodels2LDAvis(vv.8topics), out.dir="a", open.browser = FALSE)
htmltools::includeHTML("a/index.html")
```
<!--
<head>
  <script src="a/d3.v3.js"></script>
  <script src="a/ldavis.js"></script>
  <link rel="stylesheet" type="text/css" href="a/lda.css">
</head>
<body>
  <div id = "mydiv"></div>
  <script>
    var vis = new LDAvis("#mydiv", "lda.json");
  </script>
</body>
-->

<iframe width="1000" height="800" src="a/index.html" frameborder="0"></iframe>


## Sentiment Analysis

The wordcloud below gives the most popular words associated with positive and negative sentiments in the survey. Specific comments
which are associated with the most popular sentiments are listed below.

```{r swordcloud, echo=FALSE, message=FALSE, warning=FALSE}
get_sentiments_wordcloud(get_bingnrc_word_frequencies(vv.corpus.df, "bing"), "bing")
```



The  **NRC** sentiment lexicon uses categorical scale to measure 2 sentiments (positive and negative), and 8 emotions (anger, anticipation, disgust, trust, joy, sadness, fear, and suprise).
Examples of words and comments in these sentiment categories are below. In this debate, the majority of submissions were negative but also categorised as *anticipation* and *positive*. 

```{r nrc2, echo=FALSE, message=FALSE}
  plot_bingnrc_distributions(get_bingnrc_document_frequencies(vv.corpus,"nrc"), "Visitor Visa Debate", "nrc")
  
```


Hover over the plot below to read the content of the comments within each sentiment category.

```{r comments,echo=FALSE, message=FALSE, warning=FALSE }
ggplotly(display_topic_comments(get_sentiment_comments(vv.corpus.df, vv.comments, "nrc"), "Visa Debate"), width=1000, height = 600) %>% config(displayModeBar=FALSE) %>% hide_legend()
```


***


An example of a comment categorised as **negative**

  > `r vv.comments[2723,][[1]]`


An example of a comment categorised as **anticipation**

  > `r vv.comments[4143,][[1]]`


An example of a comment categorised as **positive**

  > `r vv.comments[1104,][[1]]`


